---
title: "Almond Profit Sensitivity Analysis"
author: "Erica Bishop, Colleen McCamy, Adelaide Robinson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(purrr)
library(here)
library(ggpubr)
library(viridis)

# reading in the text file
data <- read.table(here("clim.txt"), header = TRUE)

```

## Almond Profit Function 

```{r source function}

source("almond_profit.R")

```

Testing out the function:
```{r testing}

almond_profit() #using default values

almond_profit(minT2 = 5, P1 = 120) #exploring with other values

almond_profit(minT2 = 10, P1 = 0) #looking at low extremes


```
## Informal Sensitivity Analysis

Determining sensitivity of our model based on the default parameters given in Lobell et al.'s statistical model. For now, we are just looking at two coefficients - one on precipitation, one on minimum temperature.

```{r sensitivity analysis}
#parameter
beta_t1 <- -0.015
beta_p1 <- .07

#number of samples
nsamples <- 300

#standard deviation
deviation <- 0.08

#create normal distribution
beta_t1 <- rnorm(n = nsamples, mean = beta_t1, sd = deviation)
beta_p1 <- rnorm(n = nsamples, mean = beta_p1, sd = deviation)

params <- cbind.data.frame(beta_t1, beta_p1)
  
#run function across both distributions with pmap

results <- pmap(params, almond_profit)

```

```{r plot results}

results_df <- do.call(rbind, results)

results_df

beta_t1_plot <- ggplot(
  data = results_df,
  aes(x = beta_t1,
      y = profit,
      col = beta_p1)
) +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Informal sensitivity analysis",
    subtitle = "Effect of coefficient variation on almond profit",
    x = "Linear temperature coefficient",
    y = "Almond profit",
    col = "Precip coef."
  ) +
  scale_color_viridis_c(option = "magma")
  

# beta_t1_plot
  
  
beta_p1_plot <- ggplot(
  data = results_df,
  aes(x = beta_p1,
      y = profit,
      col = beta_t1)
) +
  geom_point() +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  labs(
    col = "Temp coef.",
    x = "Linear precipitation coefficient"
  )

# beta_p1_plot

ggarrange(beta_t1_plot, beta_p1_plot, ncol = 2)

```

Looking at the relationship between almond profit and the coefficients, the precipitation coefficient (beta_p1) appears to have a much stronger influence on almond profit.

